Figure Extra

### 2023-07-24 Figures/Figures_nonTCGA.Rmd
minor fixes dplyr Figures_nonTCGA.Rmd

```{r}
library(tidyverse)
library(Hmisc)
library(ggridges)
library(ggtext)
library(reshape2)
library(glue)
```

@@

```
## Corrplot
```{r}
corr <- benchmark_corr(deconv_data = deconv_GSE72056, true_estimates = truth_GSE72056, dict = dict_GSE72056, key = "Samples")
p <- plot_corrplots(store_corrs = corr, key = "Samples", title = "GSE72056")
p

>>>>

```{r}
library(tidyverse)
library(Hmisc)
library(ggridges)
library(ggtext)
library(reshape2)
library(glue)
library(ggpubr)
```

@@

```
## Corrplot
```{r}
corr <- benchmark_corrplots(deconv_data = deconv_GSE72056, true_estimates = truth_GSE72056, dict = dict_GSE72056, key = "Samples", title = "GSE72056")
corr
```
